Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
q3 explanation

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Numeric representations and soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

\begin{algorithm}[]
\begin{algorithmic}[1]
\Function{$stabilityCheck()$}{}
  \State computecharPoly($A_d - B_dK$)
  \State assert(Jury's criteria hold)
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:stabilitycheck}
\end{algorithm}

\begin{algorithm}[]
\begin{algorithmic}[1]
\Function{$safetyCheck()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
\While ($c=0; c < 2^{Num_States}; c++$)
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\While{$i=0; i< k; i++$}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndWhile
  	\State set $x_0$ to be a new vertex state
  	\EndWhile
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:safetycheck}
\end{algorithm}

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

\begin{table}
\centering
\begin{tabular}{| r | c | c | r | c | r |}
\hline
\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline

>>>>

aazZ%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Numeric representations and soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

\begin{algorithm}[]
\scriptsize
\begin{algorithmic}[1]
\Function{$stabilityCheck()$}{}
  \State computecharPoly($A_d - B_dK$)
  \State assert(Jury's criteria hold)
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:stabilitycheck}
\end{algorithm}

\begin{algorithm}[]
\scriptsize
\begin{algorithmic}[1]
\Function{$safetyCheck()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
\While ($c=0; c < 2^{Num_States}; c++$)
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\While{$i=0; i< k; i++$}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndWhile
  	\State set $x_0$ to be a new vertex state
  	\EndWhile
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:safetycheck}
\end{algorithm}

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

\begin{table}
\centering
\scriptsize
\begin{tabular}{| r | c | c | r | c | r |}
\hline
\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
